Comparison of CORD-19-trained GPT-2-based Chatbot Responses Across Different Text Semantic Similarity Approaches

### 2020-04-08 paper/paper.tex
Small improvements to the prose

Chatbots have been much studied in recent years and with the advancements in
the fields of artificial intelligence and natural language processing, both the
the functionality and the performance of these tools have seen drastic
improvements. Semantic similarity of texts, on the other hand, has been studied
for a long time and recent breakthroughs allowed employing it for a better
classification. The paper takes an approach which is really a marriage of these
two and brings a different perspective on the chatbot creation.

@@

\section{Dataset}

@@

The GPT-2 responses are usually very lengthy and for the most part, the answer
is not relevant to the question. To solve this problem, we chunked the answer
into separate sentences and found the ones that are most \textit{semantically
  similar} to the question asked. For this task, we have applied 4 different
approaches:

\begin{itemize}
  \item BioBERT large v1.1 (+PubMed 1M) model based on BERT-large Cased (custom 30k vocabulary)
  \item Universal Sentence Encoder Version 3, large
  \item Bert-Large, uncased with 24 layers and 340M parameters
  \item Scikit learn's cosine similarity
\end{itemize}

>>>>

Chatbots have been much studied in recent years and with the advancements in
the fields of artificial intelligence and natural language processing, both the
the functionality and the performance have seen drastic improvements. Semantic
similarity of texts, on the other hand, has been studied for a long time and
recent breakthroughs allowed for development of new models such as BERT,
BioBERT, and Universal Sentence Encoder. The paper takes an approach which is a
marriage of these two and brings a different perspective on the chatbot
creation. We first let a human ask a question and make GPT-2 come up with an
answer. Then we further process the answer with additional filters and
ultimately, apply a different model for finding the sentences that are most
relevant to the question.

@@

\section{Corpus}

@@

The GPT-2 responses are usually very lengthy and for the most part, the answer
is not relevant to the question. To solve this problem, we chunked the answer
into separate sentences and found the ones that are most \textit{semantically
  similar} to the question asked. For this task, we have tested and applied 4
different approaches:

\begin{itemize}
  \item BioBERT large v1.1 (+PubMed 1M) model based on BERT-large Cased (custom 30k vocabulary)
  \item Universal Sentence Encoder (USE), version 3, large
  \item Bert-Large, uncased (24 layers and 340M parameters)
  \item Scikit learn's Tfidfvectorizer
\end{itemize}
